# Coursera Assignment 1

Name: En Chieh Tseng
Date: 06/13/2015

## Data Preparation

Load data into R studio
```{r Load}
setwd('C:/Users/sauce/Desktop/Coursera/assignment 1/repdata-data-activity')
act<-read.csv('activity.csv')
str(act)
```

Remove missiong value
```{r remove_NA}
table(is.na(act))
act_new<-na.omit(act)
table(is.na(act_new))
```

## What is mean total number of steps taken per day?

Calcualte total steps per day
```{r calculation}
steps_day<-aggregate(steps~date, data=act_new, sum)
```

Create a total steps per day histogram
```{r hist}
library('ggplot2')
qplot(date,steps,data=steps_day,geom='histogram',stat='identity')+ 
        ggtitle('Total steps per day histogram')+
        theme(plot.title = element_text(lineheight=3, face="bold", size=30)
              ,axis.text.x = element_text(angle=90,size=10),axis.text.y = element_text(size=10),
              axis.title=element_text(size=12,face="bold"))
```

Mean & Median of total steps per day
```{r mean_median}
library('doBy')
summaryBy(steps~date, data=act_new, FUN=list(mean,median))
```


## What is the average daily activity pattern?

Average steps by interval
```{r steps_inter}
steps_inter<-aggregate(steps~interval,data=act_new,mean)
ggplot(steps_inter, aes(interval, steps)) + geom_line(size=1)+ggtitle('Average stpes by interval')+
        theme(plot.title = element_text(lineheight=3, face="bold", size=30),axis.text.x = element_text(size=14),
              axis.text.y = element_text(size=14),axis.title=element_text(size=14,face="bold"))
```

Which interval contains the maximum number of steps
```{r}
steps_inter$interval[which.max(steps_inter$steps)]
```


## Imputing missing values

Use mean of interval to replace missing value
